---
title: "Case Study for ``Potential bias models with Bayesian shrinkage priors for dynamic borrowing of multiple historical control data''"
author: "Tomohiro Ohigashi, Kazushi Maruo, Takashi Sozu, Ryo Sawamoto, Masahiko Gosho"
output:
  pdf_document: 
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    keep_tex: yes
documentclass: article
header-includes: 
  - \usepackage{siunitx}
  - \usepackage{zxjatype} 
  - \usepackage{booktabs} 
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage{array} 
  - \usepackage{multirow} 
  - \usepackage[ipaex]{zxjafont} 
  - \usepackage[left=30mm,right=30mm,bottom=30mm,top=35mm]{geometry}
  - \usepackage{float} \floatplacement{figure}{H} 
  - \newcommand{\beginsupplement}{\setcounter{table}{0}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \setcounter{figure}{0}
  - \renewcommand{\thefigure}{S\arabic{figure}}}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Required R packages
```{r, message = FALSE}
library(tidyverse)
library(ggpubr)
library(rstan)
library(cmdstanr)
library(bayesplot)
library(RBesT)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(knitr)
```

# Preparation
## Reading Stan Code
All Stan codes used in the case study (and simulation studies) are stored in the ``Stan'' directory.
In the following, these codes are read.
```{r}
Current_stan <- cmdstan_model(paste0(getwd(), '/Stan/Current.stan'))
Pooled_stan  <- cmdstan_model(paste0(getwd(), '/Stan/Pooled.stan'))
EX_stan      <- cmdstan_model(paste0(getwd(), '/Stan/EX.stan'))
EXNEX_stan   <- cmdstan_model(paste0(getwd(), '/Stan/EXNEX.stan'))
DPMEX_stan   <- cmdstan_model(paste0(getwd(), '/Stan/DPMEX.stan'))
DMPP_stan    <- cmdstan_model(paste0(getwd(), '/Stan/DMPP.stan'))
UIPDir_stan  <- cmdstan_model(paste0(getwd(), '/Stan/UIPDir.stan'))
HS_stan      <- cmdstan_model(paste0(getwd(), '/Stan/HS.stan'))
DL_stan      <- cmdstan_model(paste0(getwd(), '/Stan/DL.stan'))
SS_stan      <- cmdstan_model(paste0(getwd(), '/Stan/SS.stan'))
SSL_stan     <- cmdstan_model(paste0(getwd(), '/Stan/SSL.stan'))
```

## Create R function for calculating effective sample size and drawing posterior distributions for $\beta_{{\rm H}_k}$

```{r}
ess_calc3 <- function(fit){
  mix <- mixfit(fit$draws("pi_C"), type = "beta", 
                Nc = 3, constrain_gt1 =TRUE, eps = 0.01)
  ESS <- ess(mix)
  return(ESS)
}


beta_fig <- function(fit, titlevar){
  result_fit <- fit$output_files() %>% rstan::read_stan_csv()
  plot100 <- stan_dens(result_fit, pars = c("beta"))$data
  plot100_ <- plot100[order(plot100$parameter, plot100$chain),]
  plot100_1 <- plot100_ %>% filter(parameter %in%
      c("beta[1]", "beta[2]", "beta[3]", "beta[4]", "beta[5]",
        "beta[6]", "beta[7]", "beta[8]" )) %>% 
    mutate(color = case_when(
      parameter == "beta[1]" ~ "beta1",
      parameter == "beta[2]" ~ "beta2",
      parameter == "beta[3]" ~ "beta3",
      parameter == "beta[4]" ~ "beta4",
      parameter == "beta[5]" ~ "beta5",
      parameter == "beta[6]" ~ "beta6",
      parameter == "beta[7]" ~ "beta7",
      parameter == "beta[8]" ~ "beta8",
      TRUE ~ " "
    )
    )
  
  out <- ggplot(data = plot100_1, aes(x = value, color = color)) +
    labs(title = titlevar) + 
    stat_density(geom = "line", position = "identity", size = 12) +
    scale_colour_manual(
      "beta",
      values = c("#03A9F4", "#1976D2", "#4E944F", "#125B50",
                 "#D4D925", "#E8630A", "#FF0099", "#9900F0"),
      labels = c(expression(beta[1]), expression(beta[2]), 
                 expression(beta[3]), expression(beta[4]), 
                 expression(beta[5]), expression(beta[6]), 
                 expression(beta[7]), expression(beta[8]))
    ) +
    xlab(expression(beta)) +
    ylab("Density") +
    scale_x_continuous(breaks = seq(-2, 4, by = 2), limits = c(-2, 4)) + 
    scale_y_continuous(breaks = seq(0, 2, by = 1), limits = c(0, 2.5)) + 
    theme(
      plot.title = element_text(size = 240),
      axis.text = element_text(colour = "black", size = 240),
      axis.ticks=element_line(colour = "black", size = 1),
      axis.title.x = element_text(size = 240),
      axis.title.y = element_text(size = 240),
      axis.line = element_line(colour = "#000000", 
                    size = 10, linetype = "solid", lineend = "round"),
      panel.background = element_rect(fill = "transparent", colour = NA),
      panel.border = element_blank(),
      panel.grid = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 240),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.width = unit(20, "cm"),
      legend.position = c(0.8, 0.5),
      legend.key.size = unit(2, 'lines'),
      legend.spacing.x = unit(10, 'cm')
    )
  return(out)
}
```

# Case study 1 (original data)
## Datasets 

```{r}
n_h <- c(107, 44, 51, 39, 139, 20, 78, 35)
x_h <- c( 23, 12, 19,  9,  39,  6,  9, 10)
n_CC <- 6
x_CC <- 1
n_CT <- 23
x_CT <- 14

Historical <- data.frame(
  N = n_h, 
  X = x_h
)

Current <- data.frame(
  TRT = c(0, 1),
  N = c(n_CC, n_CT),
  X = c(x_CC, x_CT)
)

Data_all <- list(Historical = Historical, Current = Current)
ANA <- list(H = length(Data_all$Historical[,"N"]),
            x_h = Data_all$Historical[,"X"], n_h = Data_all$Historical[,"N"],
            x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1],
            x_CT = Data_all$Current$X[2], n_CT = Data_all$Current$N[2], 
            betascale = 1, nu = 1, C = 10)
```


## MCMC fitting

```{r, results=FALSE}
fit_Current  <- Current_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, refresh = 0)

fit_Pooled <- Pooled_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, refresh = 0)

fit_EX     <- EX_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)

fit_EXNEX  <- EXNEX_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)

fit_DPMEX  <- DPMEX_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 6000, 
        adapt_delta = 0.95, refresh = 0)

fit_DMPP   <- DMPP_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 6000, 
        adapt_delta = 0.95, refresh = 0)

gamma_h = rep(NA, length(Data_all$Historical[,"N"]))
for(h in 1:length(Data_all$Historical[,"N"])){
  gamma_h[h] = min(1, Data_all$Historical[,"N"][h] / Data_all$Current$N[1])
}

theta_h <- rep(NA, length(n_h))
I_U <- rep(NA, length(n_h))
for(h in 1:length(n_h)){
  theta_h[h] = x_h[h] * 1.0 / n_h[h]
  I_U[h] = 1 / (theta_h[h] * (1 - theta_h[h]))
}

ANA_UIP <- list(H = length(Data_all$Historical[,"N"]),
                x_h = Data_all$Historical$X, n_h = Data_all$Historical$N, 
                x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1], 
                x_CT = Data_all$Current$X[2], n_CT = Data_all$Current$N[2], 
                gamma_h = gamma_h, theta_h = theta_h, I_U = I_U)

fit_UIPDir  <- UIPDir_stan$sample(data = ANA_UIP, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 8000, 
        adapt_delta = 0.999, max_treedepth = 12, refresh = 0)


fit_HS     <- HS_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 12000, 
        adapt_delta = 0.999, refresh = 0)

ANA_DL <- list(H = length(Data_all$Historical[,"N"]),
               x_h = Data_all$Historical[,"X"], n_h = Data_all$Historical[,"N"], 
               x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1], 
               x_CT = Data_all$Current$X[2], n_CT = Data_all$Current$N[2], a = 0.5)

fit_DL <- DL_stan$sample(data = ANA_DL, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)

fit_SS     <- SS_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 6000, 
        adapt_delta = 0.95, max_treedepth = 12, refresh = 0)

ANA_SSL <- list(H = length(Data_all$Historical[,"N"]), 
                x_h = Data_all$Historical[,"X"], n_h = Data_all$Historical[,"N"], 
                x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1], 
                x_CT  =Data_all$Current$X[2], n_CT = Data_all$Current$N[2], 
                lambda_spike = 0.1, lambda_slab = 2.0)

fit_SSL <- SSL_stan$sample(data = ANA_SSL, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)
```

## Aggregate posterior distribution

```{r}

Result_ALL <- matrix(0, nrow = 11, ncol = 7)
Result_ALL[1,]  <- c(1, mean(fit_Current$draws("g_pi")), sd(fit_Current$draws("g_pi")),
                     quantile(fit_Current$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_Current$draws("g_pi"), 0.975, names = F), 
                     max(fit_Current$summary()$rhat), NA)
Result_ALL[2,]  <- c(2, mean(fit_Pooled$draws("g_pi")), sd(fit_Pooled$draws("g_pi")), 
                     quantile(fit_Pooled$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_Pooled$draws("g_pi"), 0.975, names = F), 
                     max(fit_Pooled$summary()$rhat), NA)
Result_ALL[3,]  <- c(3, mean(fit_EX$draws("g_pi")), sd(fit_EX$draws("g_pi")), 
                     quantile(fit_EX$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_EX$draws("g_pi"), 0.975, names = F), 
                     max(fit_EX$summary()$rhat), ess_calc3(fit_EX))
Result_ALL[4,]  <- c(4, mean(fit_EXNEX$draws("g_pi")), sd(fit_EXNEX$draws("g_pi")), 
                     quantile(fit_EXNEX$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_EXNEX$draws("g_pi"), 0.975, names = F), 
                     max(fit_EXNEX$summary()$rhat), ess_calc3(fit_EXNEX))
Result_ALL[5,]  <- c(5, mean(fit_DPMEX$draws("g_pi")), sd(fit_DPMEX$draws("g_pi")), 
                     quantile(fit_DPMEX$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_DPMEX$draws("g_pi"), 0.975, names = F), 
                     max(fit_DPMEX$summary()$rhat), ess_calc3(fit_DPMEX))
Result_ALL[6,]  <- c(6, mean(fit_DMPP$draws("g_pi")), sd(fit_DMPP$draws("g_pi")), 
                     quantile(fit_DMPP$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_DMPP$draws("g_pi"), 0.975, names = F), 
                     max(fit_DMPP$summary()$rhat), ess_calc3(fit_DMPP))
Result_ALL[7,]  <- c(7, mean(fit_UIPDir$draws("g_pi")), sd(fit_UIPDir$draws("g_pi")), 
                     quantile(fit_UIPDir$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_UIPDir$draws("g_pi"), 0.975, names = F), 
                     max(fit_UIPDir$summary()$rhat), ess_calc3(fit_UIPDir))
Result_ALL[8,]  <- c(8, mean(fit_HS$draws("g_pi")), sd(fit_HS$draws("g_pi")), 
                     quantile(fit_HS$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_HS$draws("g_pi"), 0.975, names = F), 
                     max(fit_HS$summary()$rhat) , ess_calc3(fit_HS))
Result_ALL[9,]  <- c(9, mean(fit_DL$draws("g_pi")), sd(fit_DL$draws("g_pi")), 
                     quantile(fit_DL$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_DL$draws("g_pi"), 0.975, names = F), 
                     max(fit_DL$summary()$rhat), ess_calc3(fit_DL))
Result_ALL[10,]  <- c(10, mean(fit_SS$draws("g_pi")), sd(fit_SS$draws("g_pi")), 
                      quantile(fit_SS$draws("g_pi"), 0.025, names = F), 
                      quantile(fit_SS$draws("g_pi"), 0.975, names = F), 
                      max(fit_SS$summary()$rhat), ess_calc3(fit_SS))
Result_ALL[11,]  <- c(11, mean(fit_SSL$draws("g_pi")), sd(fit_SSL$draws("g_pi")), 
                      quantile(fit_SSL$draws("g_pi"), 0.025, names = F), 
                      quantile(fit_SSL$draws("g_pi"), 0.975, names = F), 
                      max(fit_SSL$summary()$rhat), ess_calc3(fit_SSL))

Result_ALL1 <- as.data.frame(Result_ALL, stringsAsFactors = F)
colnames(Result_ALL1) <- c("MethodN", "Mean", "SD", "LCI", "UCI", "diag", "ESS")
Result_ALL1 <- Result_ALL1 %>% mutate(Range = (UCI - LCI)) %>%
  mutate(Method = case_when(
    MethodN == 1 ~ "CD",
    MethodN == 2 ~ "PD",
    MethodN == 3 ~ "EX",
    MethodN == 4 ~ "EXNEX",
    MethodN == 5 ~ "DPMEX",
    MethodN == 6 ~ "DMPP",
    MethodN == 7 ~ "UIP",
    MethodN == 8 ~ "PBM-HS",
    MethodN == 9 ~ "PBM-DL",
    MethodN == 10 ~ "PBM-SS",
    MethodN == 11 ~ "PBM-SSL",
    TRUE ~ ""
  )) %>%
  mutate(Mean1 = Mean * 100, SD1 = SD * 100, 
         LCI1 = LCI * 100, UCI1 = UCI * 100,
         CI1 = paste0("(", format(round(LCI * 100, digits = 1), nsmall = 1), ", ",
                      format(round(UCI * 100, digits = 1), nsmall = 1), ")")) %>% 
  mutate(EHSS1 = if_else(MethodN %in% c(1, 2), "", 
                         format(round(ESS - n_CC, digits = 1), nsmall = 1))) %>% 
  select(c(Method, Mean1, SD1, LCI1, UCI1, CI1, EHSS1)) %>% 
  mutate(case = "1")

Result_ALL1$Method <- factor(Result_ALL1$Method, 
        levels = rev(c("CD", "PD", "EX", "EXNEX", "DPMEX", "DMPP", "UIP", 
                       "PBM-HS", "PBM-DL", "PBM-SS", "PBM-SSL")))

```

## Drawing drawing posterior distributions of $\beta_{{\rm H}_k}$ for Case 1

```{r, fig.align = 'center', fig.width = 130, fig.height= 180 }

fig_HS <- beta_fig(fit_HS, "PBM-HS")
fig_DL <- beta_fig(fit_DL, "PBM-DL")
fig_SS <- beta_fig(fit_SS, "PBM-SS")
fig_SSL <- beta_fig(fit_SSL, "PBM-SSL")

fig_case1 <- ggarrange(fig_HS, fig_DL, fig_SS, fig_SSL, 
                       nrow = 4, common.legend = TRUE, legend = "bottom")

print(fig_case1)
ggsave("Beta_Case1.pdf", fig_case1, width = 9, height = 12 , bg = "white")
```

# Case study 2 (artificial data)
## Datasets 

```{r}
n_h <- c(107, 44, 51, 39, 139, 20, 78, 35)
x_h <- c( 23, 12, 31,  9,  39,  6,  9, 10)
n_CC <- 6
x_CC <- 1
n_CT <- 23
x_CT <- 14

Historical <- data.frame(
  N = n_h, 
  X = x_h
)

Current <- data.frame(
  TRT = c(0,1),
  N = c(n_CC, n_CT),
  X = c(x_CC, x_CT)
)

Data_all <- list(Historical = Historical, Current = Current)
ANA <- list(H = length(Data_all$Historical[,"N"]),
            x_h = Data_all$Historical[,"X"], n_h = Data_all$Historical[,"N"], 
            x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1], 
            x_CT = Data_all$Current$X[2], n_CT = Data_all$Current$N[2], 
            betascale = 1, nu = 1, C = 10)
```


## MCMC fitting

```{r, results=FALSE}
fit_Current  <- Current_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, refresh = 0)

fit_Pooled <- Pooled_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, refresh = 0)

fit_EX     <- EX_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)

fit_EXNEX  <- EXNEX_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)

fit_DPMEX  <- DPMEX_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 6000, 
        adapt_delta = 0.95, refresh = 0)

fit_DMPP   <- DMPP_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 6000, 
        adapt_delta = 0.95, refresh = 0)

gamma_h = rep(NA, length(Data_all$Historical[,"N"]))
for(h in 1:length(Data_all$Historical[,"N"])){
  gamma_h[h] = min(1, Data_all$Historical[,"N"][h] / Data_all$Current$N[1])
}

theta_h <- rep(NA, length(n_h))
I_U <- rep(NA, length(n_h))
for(h in 1:length(n_h)){
  theta_h[h] = x_h[h] * 1.0 / n_h[h];
  I_U[h] = 1 / (theta_h[h] * (1 - theta_h[h]));
}

ANA_UIP <- list(H = length(Data_all$Historical[,"N"]), 
                x_h = Data_all$Historical$X, n_h = Data_all$Historical$N, 
                x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1], 
                x_CT = Data_all$Current$X[2], n_CT = Data_all$Current$N[2], 
                gamma_h = gamma_h, theta_h = theta_h, I_U = I_U)

fit_UIPDir  <- UIPDir_stan$sample(data = ANA_UIP, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 8000, 
        adapt_delta = 0.999, max_treedepth = 12, refresh = 0)


fit_HS     <- HS_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 12000, 
        adapt_delta = 0.999, refresh = 0)

ANA_DL <- list(H = length(Data_all$Historical[,"N"]), 
               x_h = Data_all$Historical[,"X"], n_h = Data_all$Historical[,"N"], 
               x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1], 
               x_CT = Data_all$Current$X[2], n_CT = Data_all$Current$N[2], a = 0.5)
fit_DL <- DL_stan$sample(data = ANA_DL, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)

fit_SS     <- SS_stan$sample(data = ANA, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 6000, 
        adapt_delta = 0.95, max_treedepth = 12, refresh = 0)

ANA_SSL <- list(H = length(Data_all$Historical[,"N"]), 
                x_h = Data_all$Historical[,"X"], n_h = Data_all$Historical[,"N"], 
                x_CC = Data_all$Current$X[1], n_CC = Data_all$Current$N[1], 
                x_CT = Data_all$Current$X[2], n_CT = Data_all$Current$N[2], 
                lambda_spike = 0.1, lambda_slab = 2.0)
fit_SSL <- SSL_stan$sample(data = ANA_SSL, seed = 999, chains = 4, 
        parallel_chains = 4, iter_warmup = 4000, iter_sampling = 4000, 
        adapt_delta = 0.9, refresh = 0)
```

## Aggregate posterior distribution

```{r}

Result_ALL <- matrix(0, nrow = 11, ncol = 7)
Result_ALL[1,]  <- c(1, mean(fit_Current$draws("g_pi")), sd(fit_Current$draws("g_pi")), 
                     quantile(fit_Current$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_Current$draws("g_pi"), 0.975, names = F), 
                     max(fit_Current$summary()$rhat), NA)
Result_ALL[2,]  <- c(2, mean(fit_Pooled$draws("g_pi")), sd(fit_Pooled$draws("g_pi")), 
                     quantile(fit_Pooled$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_Pooled$draws("g_pi"), 0.975, names = F), 
                     max(fit_Pooled$summary()$rhat), NA)
Result_ALL[3,]  <- c(3, mean(fit_EX$draws("g_pi")), sd(fit_EX$draws("g_pi")), 
                     quantile(fit_EX$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_EX$draws("g_pi"), 0.975, names = F), 
                     max(fit_EX$summary()$rhat), ess_calc3(fit_EX))
Result_ALL[4,]  <- c(4, mean(fit_EXNEX$draws("g_pi")), sd(fit_EXNEX$draws("g_pi")), 
                     quantile(fit_EXNEX$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_EXNEX$draws("g_pi"), 0.975, names = F), 
                     max(fit_EXNEX$summary()$rhat), ess_calc3(fit_EXNEX))
Result_ALL[5,]  <- c(5, mean(fit_DPMEX$draws("g_pi")), sd(fit_DPMEX$draws("g_pi")), 
                     quantile(fit_DPMEX$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_DPMEX$draws("g_pi"), 0.975, names = F), 
                     max(fit_DPMEX$summary()$rhat), ess_calc3(fit_DPMEX))
Result_ALL[6,]  <- c(6, mean(fit_DMPP$draws("g_pi")), sd(fit_DMPP$draws("g_pi")), 
                     quantile(fit_DMPP$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_DMPP$draws("g_pi"), 0.975, names = F), 
                     max(fit_DMPP$summary()$rhat), ess_calc3(fit_DMPP))
Result_ALL[7,]  <- c(7, mean(fit_UIPDir$draws("g_pi")), sd(fit_UIPDir$draws("g_pi")), 
                     quantile(fit_UIPDir$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_UIPDir$draws("g_pi"), 0.975, names = F), 
                     max(fit_UIPDir$summary()$rhat), ess_calc3(fit_UIPDir))
Result_ALL[8,]  <- c(8, mean(fit_HS$draws("g_pi")), sd(fit_HS$draws("g_pi")), 
                     quantile(fit_HS$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_HS$draws("g_pi"), 0.975, names = F), 
                     max(fit_HS$summary()$rhat) , ess_calc3(fit_HS))
Result_ALL[9,]  <- c(9, mean(fit_DL$draws("g_pi")), sd(fit_DL$draws("g_pi")), 
                     quantile(fit_DL$draws("g_pi"), 0.025, names = F), 
                     quantile(fit_DL$draws("g_pi"), 0.975, names = F), 
                     max(fit_DL$summary()$rhat), ess_calc3(fit_DL))
Result_ALL[10,]  <- c(10, mean(fit_SS$draws("g_pi")), sd(fit_SS$draws("g_pi")), 
                      quantile(fit_SS$draws("g_pi"), 0.025, names = F), 
                      quantile(fit_SS$draws("g_pi"), 0.975, names = F), 
                      max(fit_SS$summary()$rhat), ess_calc3(fit_SS))
Result_ALL[11,]  <- c(11, mean(fit_SSL$draws("g_pi")), sd(fit_SSL$draws("g_pi")), 
                      quantile(fit_SSL$draws("g_pi"), 0.025, names = F), 
                      quantile(fit_SSL$draws("g_pi"), 0.975, names = F), 
                      max(fit_SSL$summary()$rhat), ess_calc3(fit_SSL))

Result_ALL2 <- as.data.frame(Result_ALL,stringsAsFactors = F)
colnames(Result_ALL2) <- c("MethodN", "Mean", "SD", "LCI", "UCI", "diag", "ESS")
Result_ALL2 <- Result_ALL2 %>% mutate(Range = (UCI - LCI)) %>%
  mutate(Method = case_when(
    MethodN == 1 ~ "CD",
    MethodN == 2 ~ "PD",
    MethodN == 3 ~ "EX",
    MethodN == 4 ~ "EXNEX",
    MethodN == 5 ~ "DPMEX",
    MethodN == 6 ~ "DMPP",
    MethodN == 7 ~ "UIP",
    MethodN == 8 ~ "PBM-HS",
    MethodN == 9 ~ "PBM-DL",
    MethodN == 10 ~ "PBM-SS",
    MethodN == 11 ~ "PBM-SSL",
    TRUE ~ ""
  )) %>%
  mutate(Mean1 = Mean * 100, SD1 = SD * 100, 
         LCI1 = LCI * 100, UCI1 = UCI * 100,
         CI1 = paste0("(", format(round(LCI * 100, digits = 1), nsmall = 1), ", ",
                      format(round(UCI * 100, digits = 1), nsmall = 1), ")")) %>% 
  mutate(EHSS1 = if_else(MethodN %in% c(1, 2), "", 
                         format(round(ESS - n_CC, digits = 1), nsmall = 1))) %>% 
  select(c(Method, Mean1, SD1, LCI1, UCI1, CI1, EHSS1)) %>% 
  mutate(case = "2")

Result_ALL2$Method <- factor(Result_ALL2$Method, 
        levels = rev(c("CD", "PD", "EX", "EXNEX", "DPMEX", "DMPP", "UIP", 
                       "PBM-HS", "PBM-DL", "PBM-SS", "PBM-SSL")))

```

## Drawing drawing posterior distributions of $\beta_{{\rm H}_k}$ for Case 2

```{r, fig.align = 'center', fig.width = 130, fig.height= 180 }

fig_HS <- beta_fig(fit_HS, "PBM-HS")
fig_DL <- beta_fig(fit_DL, "PBM-DL")
fig_SS <- beta_fig(fit_SS, "PBM-SS")
fig_SSL <- beta_fig(fit_SSL, "PBM-SSL")

fig_case2 <- ggarrange(fig_HS, fig_DL, fig_SS, fig_SSL, nrow = 4, 
                       common.legend = TRUE, legend = "bottom")

print(fig_case2)
ggsave("Beta_Case2.pdf", fig_case2, width = 9, height = 12 ,bg = "white")
```


# Create output
```{r, eval = knitr::is_latex_output()}
Res_ALL <- rbind(Result_ALL1, Result_ALL2)

Res_ALL_out <- Res_ALL %>%
  select(-c(LCI1, UCI1)) %>% 
  pivot_wider(names_from = case, values_from = c(Mean1, SD1, CI1, EHSS1), 
              names_sep = "_") %>%
  select(Method, Mean1_1, SD1_1, CI1_1, EHSS1_1, Mean1_2, SD1_2, CI1_2, EHSS1_2)
write.csv(Res_ALL_out, file = "Result.csv", row.names = FALSE)

kable(Res_ALL_out, align = c("lrrcrrrcr"), digits = 1, 
      format = "latex", escape = F,
      caption = "Summary of posterior distributions of the treatment effect, $\\pi_{\\rm CT}-\\pi_{\\rm CC} (\\%)$, for cases 1 (original dataset) and 2 (artificial dataset).",
      label = "tab1",
      col.names = c("Method", "Mean", "SD", "95\\%CI", "EHSS", 
                    "Mean", "SD", "95\\%CI", "EHSS"),
      row.names = FALSE,
      booktabs = T, linesep = "") %>% 
      kable_styling(font_size = 11, latex_options = c("hold_position")) %>% 
      add_footnote("SD: standard deviation; CI: credible interval; CD: current data analysis; PD: pooled data analysis; EX: full exchangeability MAC method; EXNEX: exchangeability--non-exchangeability MAC method; DPMEX: Dirichlet process mixture of exchangeability MAC method; DMPP: dependent modified power prior; UIP: unit information prior; PBM-HS: potential bias model with horseshoe prior; PBM-DL: potential bias model with Dirichlet--Laplace prior; PBM-SS: potential bias model with spike-and-slab prior; PBM-SSL: potential bias model with spike-and-slab Lasso prior.", 
      notation = "none", threeparttable = T) %>%
      add_header_above(c(" ", "Case 1" = 4, "Case 2" = 4))
```

## Drawing forest plot

```{r}
labeli <- as_labeller(c("1" = "Case 1", "2" = "Case 2"))

Res_ALL_fig <- Res_ALL
Res_ALL_fig[Res_ALL_fig$Method == "PD", "EHSS1"] <- "EHSS"

Result_fig <- ggplot(Res_ALL_fig, aes(x = Mean1, y = Method)) +
  xlab("Treatment effect in terms of the response rate (%)") +
  geom_point(size = 3) +
  geom_linerange(aes(xmin = LCI1, xmax = UCI1), size = 1) +
  coord_cartesian(xlim = c(0, 80), expand = T) +
  geom_text(aes(x = 70, label = EHSS1), hjust = 0, size = 4) +
  theme(
    plot.title = element_blank(),
    axis.text.x = element_text(colour = "black", size = 10),
    axis.text.y = element_text(colour = "black", size = 10),
    axis.ticks.x = element_line(colour = "black", size = 1),
    axis.ticks.y = element_line(colour = "black", size = 1),
    axis.title.x = element_text(colour = "black", size = 16),
    axis.title.y = element_blank(),
    axis.line.x = element_line(colour = "#000000", size = 1, 
                          linetype = "solid", lineend = "round"),
    axis.line.y = element_line(colour = "#000000", size = 1, 
                          linetype = "solid", lineend = "round"),
    panel.background = element_rect(fill = "transparent", colour = NA),
    panel.border = element_blank(),
    panel.grid = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank()
  ) +
  facet_grid( ~ case, scales = "fixed", space = "free", 
              labeller = labeli, switch = "y") +
  theme(
    strip.placement.y = "outside",
    strip.background = element_blank(),
    strip.text.x = element_text(colour = "black", size = 16),
    panel.spacing.y = unit(1.5, "lines")
  )
```

```{r, fig.align = 'center', out.width="100%"}
print(Result_fig)
ggsave("Result.pdf", Result_fig, width = 12, height = 8, bg = "white")
```


